On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-02-14 article/ms.tex
Added Johns comments plus more issues

One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released by Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the normal [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}. Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning. However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}. Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.

@@

Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples. For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee. Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}. We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity. We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single particular stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.

@@

Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances. However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption. It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a positive correlation between Na and K. No relation between Na and K abundances is observed.

@@

An early modelling attempt to replicate the anomalous Mg--K abundance ratios assumed hot-bottom burning in asymptotic giant branch (AGB) and super-AGB (SAGB) stars. \cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected by \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the Ar--K reaction cross section was increased to 100 that measured in the laboratory, or if the temperature at the base of the envelope could be made to exceed 150\,MK.

@@

\section{Conclusions}
\label{sec:conclusion}
From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and depleted in Mg. Stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808; this work represents the first observations of field stars with this peculiar abundance signature. Our candidates are not restricted to a particular phase of stellar evolution, and their metallicity distribution is reflective of the parent \lamost\ sample.

>>>>

One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released by Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the normal [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419. In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing some reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}. Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.  Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning. However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.

@@

Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples. For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee. Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}. We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity. We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.

@@

Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances. However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption. It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K. No relation between Na and K abundances is observed.

@@

An early modelling attempt to replicate the anomalous Mg--K abundance ratios assumed hot-bottom burning in asymptotic giant branch (AGB) and super-AGB (SAGB) stars. \cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (\cite{ventura2012} corrected by \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the Ar--K reaction cross section was increased to 100 that measured in the laboratory, or if the temperature at the base of the envelope could be made to exceed 150\,MK.

@@

\section{Conclusions}
\label{sec:conclusion}
From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and potentially depleted in Mg. Stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808; this work represents the first observations of field stars with this peculiar abundance signature. Our candidates are not restricted to a particular phase of stellar evolution, and their metallicity distribution is reflective of the parent \lamost\ sample.
